Analysis for Performing-Dynamics performances (Key Velocity)

### 2020-05-13 material/analysis/expression/stim_d/kv.Rmd
add seq plot
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

#### Sequence plot
- Right wrap: Subject Number

>>>>

### Sequence plot
- Right wrap: Subject Number

#### All
```{r kv_seq, fig.width = 14, fig.height = 12, echo = FALSE}
# for each individual
dt_kv$TrialNr <- as.factor(dt_kv$TrialNr)
kv_seq <- dt_kv[Subcomponent != "NA", .(N = length(Velocity), Mean = mean(Velocity)), by = .(SubNr, TrialNr, RowNr)]

p_kv_seq <- ggplot(data = kv_seq, aes(x = RowNr, y = Mean, group = TrialNr, colour = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Velocity", subtitle = "KV: Performing-Dynamics(All)") +
  scale_x_continuous(breaks=seq(1,66,1)) + scale_y_continuous(breaks=seq(0,2,0.5), limits = c(0, 2))
p_kv_seq
```
